Pythran: Bringing OpenMP to a Python Subset

### 2013-01-29 doc/papers/europar2013/paper.tex
WIP

This hybrid approach, based on a mix of interpreted and native code, is getting
wide spread in the Python landscape. Section~\ref{sec:python-parallel} studies the
existing approaches and shows a critical lack of parallelism support.
Section~\ref{sec:python-openmp} studies the validity of adding OpenMP directives to the
Python language in order to add fine-grain parallelism support to Python in the
context of a Python subset called Pythran. Static compilation of this language
into C++ and the underlying runtime is described in
Section~\ref{sec:python-static-translation}.
Section~\ref{sec:python-optim} presents several optimizations applied by the compiler to
optimized generated code with respect to parallelism. The Pythran compiler is
benchmarked on several scientific applications and compared to both interpreted
and native code in Section~\ref{sec:validation}.

@@

\subsection{Variable Scope}

\subsection{Iterators}

>>>>

This hybrid approach, based on a mix of interpreted and native code, is getting
wide spread in the Python landscape. Section~\ref{sec:python-parallel} studies the
existing approaches and shows a critical lack of parallelism support.
Section~\ref{sec:python-openmp} studies the validity of adding OpenMP directives to the
Python language in order to add fine-grain parallelism support to Python in the
context of a Python subset called Pythran. Static compilation of this language
into C++ and the underlying runtime is described in
Section~\ref{sec:python-static}.
Section~\ref{sec:python-optim} presents several optimizations applied by the compiler to
optimized generated code with respect to parallelism. The Pythran compiler is
benchmarked on several scientific applications and compared to both interpreted
and native code in Section~\ref{sec:validation}.

@@

OpenMP is a standard API for parallel programming for Fortran, C and C++.

\subsection{Directives}

\subsubsection{Variable Scope}

\subsubsection{Iterators}

\subsection{Runtime Library}

\subsection{Validation}

\cite{wang2012}
